\section{Work Experience}
\begin{itemize}
  \item 2020:
    \begin{itemize}
      \item Reviewer at the Thirteen Latin America 
        Workshop on New Methods of Reasoning 2020. 
        \url{http://www.lanmr.unam.mx/}
    \end{itemize}
  \item 2019:
    \begin{itemize}
      \item Teaching Assistant at the University of New Mexico. Graduate level
        Geometric and Probabilistic Methods in Computer Science.
      \item Summer Research Intern at Microsoft Research.
      \item Reviever at the 35th International Conference on Logic Programming
        2019. \url{https://www.cs.nmsu.edu/ALP/iclp2019/}
      \item Teaching Assistant at the University of New Mexico. Graduate level
        Theory of Computation.
    \end{itemize}
  \item 2018:
    \begin{itemize}
      \item Teaching Assistant at the University of New Mexico. Graduate level
        Algorithms and Data Structures.
      \item PC member at the 11th Latin American Workshop on New Methods of
        Reasoning 2018. \url{https://lanmr.cs.buap.mx}
      \item Reviewer at the 14th Annual Computer Science Student Conference
        2018. \url{https://www.cs.unm.edu/~csgsa/2017-2018/papers.html}
    \end{itemize}
  \item 2017:
    \begin{itemize}
      \item Reviewer at the 17th Latin American Symposium on Mathematical
        Logic. \url{http://www.fcfm.buap.mx/SLALM2017/}
    \end{itemize}
  \item 2016:
    \begin{itemize}
      \item Reviewer at the 10th Latin American Workshop on Logic/Languages,
        Algorithms and New Methods of Reasoning. \url{http://ceur-ws.org/Vol-1659/}
      \item Reviewer at the 8th Mexican Congress on Artificial Intelligence.
        \url{https://www.comia.org.mx/2016/}
    \end{itemize}
  \item 2015:
    \begin{itemize}
      \item Reviewer at the 12th International Colloquium on Theoretical
        Aspects of Computing. \url{http://www.ictac2015.co/}
    \end{itemize}
  \item 2014:
    \begin{itemize}
      \item Intern, Innova4D. I worked and analysed graph algorithms to
        compute Freeman centralities for the development of a recommendation
        system.
    \end{itemize}
\end{itemize}

